Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-24 Methods.tex
Starting in on results

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing (section \ref{sub:info_sharing}) on the robustness of these trends. Table \ref{tab:sharing_params} gives the parameters explored, with a more complete exploration of the effects on the system as a whole performed as part of the global sensitivity analysis.

\begin{table}
\center
\begin{tabular} {|l | l | l| l| l|}
\hline
Name & Description & Min & Max & Step Size \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 & 0.25 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 & 0.25 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 & 0.25 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 & 0.25 \\ \hline
\end{tabular}
\caption[Table caption text]{Information sharing parameter ranges. \label{tab:sharing_params}}
\end{table}

>>>>

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w}\,\&\,w_{w}={0.25, 0.5, 0.75, 1}\).

### 2014-07-24 Model.tex
Progress!
Stigma, notation
Wordings
Starting in on results

%!TEX root = disclosure_game.tex
\section{Model}
\label{sec:model}
%Start this off with a brief description of our fictional scenario.
% Whole section ~ 1.5K

In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife. 
Typically women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However even when considering less emotive topics, this is not the case.

@@

Where $X$ is set of payoffs the agent has observed to follow $s$.

@@

\begin{equation}
R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(s_{m,i})p(i | s_{w})
\end{equation}

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
\end{equation}

>>>>

%!TEX root = disclosure_game.tex
\section{Disclosure Game Model}
\label{sec:model}
%Start this off with a brief description of our fictional scenario.
% Whole section ~ 1.5K

In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife.

Typically women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{Radcliffe2011,NICE2010}.

@@

Where $X$ is the set of payoffs the agent has observed to follow $s$.

@@

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})
\end{equation}

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i, \theta_{m})p(i | s_{w})
\end{equation}

### 2014-07-24 Results.tex
Starting in on results

LOOK AT MAH GRAFS!

@@

As shown in figure \ref{fig:qt_honesty}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:qt_ref}), which show that the majority of drinkers are referred, despite substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.

\begin{figure}[h!]
\caption{Average fraction of population signalling honestly over appointments, across 100 runs.}
\label{fig:qt_honesty}
\end{figure}

\begin{figure}[h!]
\caption{Average fraction of population referred over appointments, across 100 runs.}
\label{fig:qt_ref}
\end{figure}

>>>>

@@

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, despite substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

\begin{figure}[h!]
\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot.png}

}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot.png}}\end{adjustbox}
\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
\label{fig:qt_trends}
\end{figure}
